Hydras \& Co.

### 2022-03-04 doc/part-hydras.tex
unification of T1add and T1mul names

\paragraph{\gaiacompat (cf. Remark ~\ref{remark:hydra-gaia-renaming})}
In \gaia, addition and multiplication of ordinal terms below $\epsilon_0$ are respectively called \texttt{T1add} and \texttt{T1mul}. Please refer to Sect.~\ref{sect:plus-mult-gaia-hydras} about compatibility of both arithmetics.

>>>>

\paragraph{\gaiacompat (cf. Remark ~\ref{remark:hydra-gaia-renaming})}
We keep \gaia's base names for
addition and multiplication of ordinal terms below $\epsilon_0$.
Please refer to Sect.~\ref{sect:plus-mult-gaia-hydras} about compatibility of both arithmetics.
